---
title: "Week 12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# Same data clean up as last week.

week_12 <- shaming %>% 
  mutate(age = 2006 - birth_year) %>% 
  mutate(treatment = fct_relevel(treatment, "Control")) %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(-general_04, -no_of_names, -birth_year, -hh_size) 

week_12_sample <- sample_n(week_12, 1000)
```


## Scene 1

**Prompt:** Create a fitted model object called `fit_1` using this formula or, if you want, a formula which you prefer. You are trying to model `age` as a function of various parameters.

age ~ sex + solo + primary_04 + primary_06 + treatment + sex:solo
                    
* Is this a causal or predictive model? Why?

* Interpret the fitted model. 

* Should we keep all these variables? And the interaction term?

* Are you surprised about the meaningfulness, or lack thereof, for the treatment variables?


```{r sc1}

fit_1 <- stan_glm(age ~ sex + solo + sex:solo,
         data = week_12_sample,
         refresh = 0,
         seed = 9)

print(fit_1, digits = 5)

```
Intercept: A female in the control group that does not live alone.
sexMale: The predicted difference in average age between males and females, is 1.4983.
soloTRUE: The predited difference in average age between the intercept and females that live alone. Is 9.76.
Interaction term: Just looking at males living alone, instead of males living with people or females living alone. The unique effect of being both male and living alone.
primary_04Yes: The predicted difference in age between intercept and people in the control group that voted in the primary.






## Scene 2

**Prompt:** Provide a posterior probability distribution for the expected difference in ages between those who live alone and those who do not. (Hint: Given that we are asking for an expected value, use `posterior_epred()`.)







